Simulations, CLT and EVT

### 2020-08-27 mean_null.Rmd
minor change

Samples are taken from Gamma(3, 0.5) distribution and $k = 500$ in all the cases. Small values of n considered in the range  ${2, 3, \ldots, 10}$ and large values of $n$ considered within ${25, 30, 35, \ldots, 45}$. We study the distribution of:

@@

Q: So when we are talking about normalising for the levels when number of levels are low? - Not by using limit theorems. Transformation?

@@

```{r shape_rate}
shape1 = 3
rate1 = 0.5
```

@@

create_simdata <- function(nx = 2,
                           # number of rvs to generate
                           nsim = 500,
                           # number of simulations
                           sim_dist = distributional::dist_gamma(shape = shape1, 
                                                                 rate = rate1),
                           # distribution of each rv
                           create_fun = mean
                           # function used on the rvs
) {
  mean_dist <- (1:nsim) %>%
    purrr::map(function(i) {
      x <- sim_dist %>%
        distributional::generate(nx) %>%
        unlist()
      x %>% create_fun()
    })
}
```

@@

plot_simdata <- function(nlevels = seq(2, 10, 1),
                         nsim = 500,
                         sim_dist = distributional::dist_gamma(shape = shape1,
                      rate = rate1),
                         # distr = "norm",
                         create_fun = mean) {
  data_orig <- nlevels %>%
    purrr::map_df(function(i) {
      create_datai <- create_simdata(nx = i, nsim, sim_dist, create_fun)
      tibble::tibble(ind = i, sim_data = create_datai)
    })

>>>>

Samples are taken from Gamma(shape = 3, rate = 0.5) distribution and $k = 500$ in all the cases. Small values of n considered in the range  ${2, 3, \ldots, 10}$ and large values of $n$ considered within ${25, 30, 35, \ldots, 45}$. We study the distribution of:

@@

Question: So we cannot normalise for the number of levels using limit theorems when we are talking about normalising for few levels? By normalisation, if we mean adjusting values measured on different scales to a common scale, then that could be done through limit theorems. If the intention is to align distributions to a normal like distribution, then we have to resort to something else like distribution transformation?

@@

```{r shape_rate}
shape1 <- 3
rate1 <- 0.5
```

@@

create_simdata <- function(nx = 2,
                           # number of rvs to generate
                           nsim = 500,
                           # number of simulations
                           sim_dist = distributional::dist_gamma(
                             shape = shape1,
                             rate = rate1
                           ),
                           # distribution of each rv
                           create_fun = mean
                           # function used on the rvs
) {
  mean_dist <- (1:nsim) %>%
    purrr::map(function(i) {
      x <- sim_dist %>%
        distributional::generate(nx) %>%
        unlist()
      x %>% create_fun()
    })
}
```

@@

plot_simdata <- function(nlevels = seq(2, 10, 1),
                         nsim = 500,
                         sim_dist = distributional::dist_gamma(
                           shape = shape1,
                           rate = rate1
                         ),
                         # distr = "norm",
                         create_fun = mean) {
  data_orig <- nlevels %>%
    purrr::map_df(function(i) {
      create_datai <- create_simdata(nx = i, nsim, sim_dist, create_fun)
      tibble::tibble(ind = i, sim_data = create_datai)
    })
